---
title: "DVCR Forum with MCRs (July 2025)"
subtitle: "Summary of Responses to RDS Survey: Complete Report"
#author: "Jen Beaudry"
#date: "24/03/2026"
output: pdf_document
editor_options: 
  chunk_output_type: console
header-includes:
  - \usepackage{caption}
  - \usepackage{titling}
    \setlength{\droptitle}{-2cm} # removes some of the white space above title
  - \pretitle{\begin{center}
    \includegraphics[width=1.5in, height=0.5in]{flinders-university-horizontal-master.png}\LARGE\\} # adds logo
  - \posttitle{\end{center}}
  - \usepackage{fancyhdr}
  - \fancypagestyle{plain}{\pagestyle{fancy}} # sets the footer on page 1
  - \pagestyle{fancy} # sets the footer on page 2 and beyond
  - \fancyhf{} # clears existing header & footer
  - \renewcommand{\headrulewidth}{0pt} # removes the line from the header
  - \fancyfoot[R]{\thepage} # page number in foooter
---

```{r setup, include=FALSE}

### NOTE: USE THIS FOR THE FULL REPORT ###

knitr::opts_chunk$set(echo = FALSE,
                      include = TRUE, 
                      eval = TRUE)

# REMEMBER: Until you figure out parameterized reports, you'll have to manually 
  # select which chunks to run and will need to delete the 'empty pages' that 
  # aren't included in Rob's report

```

```{r library, include=FALSE}

library(here)
library(tidyverse)
library(kableExtra)
library(RColorBrewer)

```

```{r functions, include=FALSE}

styler_pdf <- function(dat) {
  dat %>%
     kable_styling(full_width = F, 
                latex_options = c("striped", "HOLD_position"))
}

source(here("..", "functions", "ratings_summary.R"))

```

```{r load data, include=FALSE}

df <- read_csv(here::here("data", "mcr_forum_processed.csv"), lazy = FALSE)

# get this data from the spreadsheet
attendees <- as.integer(39)

```

We asked our attendees five questions. Three were about the forum, one was about
other training and development offerings that they would like, and one was an open-ended 
question giving them a chance to tell us anything else they wanted us to know. 

Of the `r attendees` mid-career researchers who attended this session, `r nrow(df)` 
completed the survey. The responses might not be reflective of the attitudes of 
all attendees because of the relatively low response rate (`r round((nrow(df)/attendees*100),2)`%).

It's important to keep in mind the context in which this forum was held. This year, 
the University implemented a university-wide academic workload model, which has 
had a considerable impact on the academic community. As such, some of the questions 
in the forum related to having enough time to conduct research and supervise 
HDR students in the face of increased teaching demands; however, this was less 
of a focus in the MCR Forum than it was in the ECR Forum. 

\captionsetup[table]{labelformat=empty}


## Feedback about today's DVC(R) forum with MCRs
What did you think about today's forum?

```{r table for feedback}

# use for complete report and report for DVCR

# put relevant data in a tibble
feedback <- df %>% 
  dplyr::select(c(id, feedback)) %>% 
  filter(!feedback == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(feedback$id))
ns <- c(total_n, resp_n) 

feedback <- feedback %>% 
  dplyr::select(c(id, feedback))

knitr::kable (
  feedback,
    format = "latex",
  escape = F,
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "MCR Forum Feedback"),
  caption =
    sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 
# use different styling to repeat the header


```


\captionsetup[table]{labelformat=empty}

## Takeaways from the MCR Forum
What is one new thing that you learned from today's forum?

```{r table for new_thing}

# use for complete report and report for DVCR

# put relevant data in a tibble
new_thing <- df %>% 
  dplyr::select(c(id, new_thing)) %>% 
  filter(!new_thing == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(new_thing$id))
ns <- c(total_n, resp_n) 

new_thing <- new_thing %>% 
  dplyr::select(c(id, new_thing))

knitr::kable (
  new_thing,
  format = "latex",
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "What's one new thing that you learned?"),
  caption =
    sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 
# use different styling to repeat the header


```

\newpage
## Ideas for the DVC(R) forum with MCRs
What would you like to see in future fora with the DVC(R)?

```{r table for forum ideas}

# use for complete report and report for DVCR

# put relevant data in a tibble
forum_ideas <- df %>% 
  dplyr::select(c(id, future_fora)) %>% 
  filter(!future_fora == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(forum_ideas$id))
ns <- c(total_n, resp_n) 

forum_ideas <- forum_ideas %>% 
  dplyr::select(c(id, future_fora))

knitr::kable (
  forum_ideas,
  format = "latex",
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Ideas for future MCR Fora"),
  caption =
    sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 
# use different styling to repeat the header


```


## Ideas for other training and development opportunities
What other researcher training and development opportunities would you like to see
at Flinders?

```{r table for other training}

# put relevant data in a tibble
other_training <- df %>% 
  dplyr::select(c(id, training)) %>% 
  filter(!training == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(other_training$id))
ns <- c(total_n, resp_n) 

other_training <- other_training %>% 
  dplyr::select(c(id, training))

knitr::kable (
  other_training,
  format = "latex",
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Other Training Ideas"),
  caption =
    sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 
# use different styling to repeat the header


```


\captionsetup[table]{labelformat=empty}

## Final comments
Is there anything else you would like us to know?

```{r table for anything else}

# put relevant data in a tibble
anything <- df %>% 
  dplyr::select(c(id, anything_else)) %>% 
  filter(!anything_else == "NA") %>%  # remove the NA values
  mutate(responses = 1:n()) %>% 
  relocate(responses, .after = id)

# get the relevant ns for the header
total_n <- length(unique(df$id))
resp_n <- length(unique(anything$id))
ns <- c(total_n, resp_n) 

anything <- anything %>% 
  dplyr::select(c(id, anything_else))

knitr::kable (
  anything,
  format = "latex",
  booktabs = T,
  linesep = "\\addlinespace",
  col.names = c("ID", "Other Ideas"),
  caption =
   sprintf("From the %s people responded to this question", paste(ns, collapse = " completed surveys, ")),
  align = 'cl', 
  longtable = T #break the table over multiple pages
  ) %>%
  column_spec(2, width = "5.5in") %>% 
  kable_styling(full_width = F, 
                latex_options = c("repeat_header", "hold_position", "striped")) 
# use different styling to repeat the header


```

If you have any questions, please contact Dr Jen Beaudry, Manager, Researcher Training, Development and Communication in Research Development and Support. 
